Cheminformatics: The Computer Science of Chemical Discovery

### 2011-08-15 paper.tex
Added proper math symbol

The major difficulty with enumeration (apart from the size of the search space, which is thought to be in the order of 10^60 molecules for 30 heavy atoms) is that the \emph{in silico}
representation of molecules, the so-called molecular graphs, are
labeled objects (i.e. labeled graphs), while the atoms of a molecule
are of course not uniquely labeled. The mathematical concept to tackle
this problem is to consider orbits of labeled molecular graphs under
the operation of the symmetric group. However, when enumerating molecular
structures, one has thus to solve the so--called isomorphism problem, where molecules that seem different are actually equivalent (i.e., their atoms can be mapped on top of each other by keeping the connectivity between atoms intact).
The good news is that isomorphism can be solved in polynomial time for
molecular graphs due to the fact that molecules belong to a restricted
class of graphs known as \emph{bounded valence graphs}; however, that
same restriction prevents applying to a molecular graph the polynomial
delay enumeration results obtained for general graphs (Chapter 8 in
\cite{faulon2010}). While the complexity of molecular graph
enumeration remains an open problem it has nonetheless been shown that
molecules can be sampled efficiently \cite{goldberg1999}. Sampling
procedures based on the Metropolis or the Genetic Algorithms have been
developed and used to elucidate natural compounds from NMR data.

>>>>

The major difficulty with enumeration (apart from the size of the search space, which is thought to be in the order of $10^60$ molecules for 30 heavy atoms) is that the \emph{in silico}
representation of molecules, the so-called molecular graphs, are
labeled objects (i.e. labeled graphs), while the atoms of a molecule
are of course not uniquely labeled. The mathematical concept to tackle
this problem is to consider orbits of labeled molecular graphs under
the operation of the symmetric group. However, when enumerating molecular
structures, one has thus to solve the so--called isomorphism problem, where molecules that seem different are actually equivalent (i.e., their atoms can be mapped on top of each other by keeping the connectivity between atoms intact).
The good news is that isomorphism can be solved in polynomial time for
molecular graphs due to the fact that molecules belong to a restricted
class of graphs known as \emph{bounded valence graphs}; however, that
same restriction prevents applying to a molecular graph the polynomial
delay enumeration results obtained for general graphs (Chapter 8 in
\cite{faulon2010}). While the complexity of molecular graph
enumeration remains an open problem it has nonetheless been shown that
molecules can be sampled efficiently \cite{goldberg1999}. Sampling
procedures based on the Metropolis or the Genetic Algorithms have been
developed and used to elucidate natural compounds from NMR data.
